\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-04-13 jss/article.tex
n - > round(n)

           sample.mean        n prior.mean shrinkage intv.low post.mean intv.upp post.sd
1                0.045   67.000       0.02     0.834    0.011     0.024    0.042   0.008
2                0.029   68.000       0.02     0.832    0.010     0.022    0.038   0.007
3                0.024  210.000       0.02     0.616    0.011     0.021    0.035   0.006
4                0.043  256.000       0.02     0.568    0.017     0.030    0.046   0.008
5                0.033  269.000       0.02     0.556    0.015     0.026    0.041   0.007
6                0.044  274.000       0.02     0.551    0.018     0.031    0.047   0.008
7                0.043  278.000       0.02     0.548    0.018     0.030    0.047   0.007
8                0.014  295.000       0.02     0.533    0.008     0.017    0.029   0.005
9                0.029  347.000       0.02     0.492    0.014     0.024    0.038   0.006
10               0.037  349.000       0.02     0.491    0.017     0.029    0.043   0.007
11               0.039  358.000       0.02     0.484    0.018     0.030    0.045   0.007
12               0.018  396.000       0.02     0.459    0.010     0.019    0.030   0.005
13               0.028  431.000       0.02     0.438    0.015     0.024    0.037   0.006
14               0.025  441.000       0.02     0.433    0.013     0.023    0.035   0.005
15               0.027  477.000       0.02     0.414    0.015     0.024    0.036   0.006
16               0.045  484.000       0.02     0.410    0.023     0.035    0.050   0.007
17               0.030  494.000       0.02     0.405    0.016     0.026    0.039   0.006
18               0.022  501.000       0.02     0.402    0.012     0.021    0.032   0.005
19               0.028  505.000       0.02     0.400    0.015     0.025    0.036   0.005
20               0.020  540.000       0.02     0.384    0.012     0.020    0.031   0.005
21               0.028  563.000       0.02     0.374    0.016     0.025    0.037   0.005
22               0.024  593.000       0.02     0.362    0.014     0.022    0.033   0.005
23               0.015  602.000       0.02     0.358    0.010     0.017    0.026   0.004
24               0.024  629.000       0.02     0.348    0.014     0.023    0.033   0.005
25               0.020  636.000       0.02     0.346    0.012     0.020    0.030   0.005
26               0.048  729.000       0.02     0.316    0.027     0.039    0.053   0.007
27               0.031  849.000       0.02     0.284    0.019     0.028    0.038   0.005
28               0.027  914.000       0.02     0.269    0.017     0.025    0.035   0.005
29               0.021  940.000       0.02     0.264    0.014     0.021    0.030   0.004
30               0.029 1193.000       0.02     0.220    0.020     0.027    0.036   0.004
31               0.020 1340.000       0.02     0.201    0.014     0.020    0.027   0.003
== Mean ==       0.029  517.032       0.02     0.438    0.015     0.025    0.037   0.006
\end{CodeOutput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.3]{hospital1.png}
\caption{Shrinkage and interval plots of 31 hospitals in NY}
\end{center}
\end{figure}

>>>>

         obs.mean        n prior.mean shrinkage intv.low post.mean intv.upp post.sd
1           0.045   67.000       0.02     0.834    0.011     0.024    0.042   0.008
2           0.029   68.000       0.02     0.832    0.010     0.022    0.038   0.007
3           0.024  210.000       0.02     0.616    0.011     0.021    0.035   0.006
4           0.043  256.000       0.02     0.568    0.017     0.030    0.046   0.008
5           0.033  269.000       0.02     0.556    0.015     0.026    0.041   0.007
6           0.044  274.000       0.02     0.551    0.018     0.031    0.047   0.008
7           0.043  278.000       0.02     0.548    0.018     0.030    0.047   0.007
8           0.014  295.000       0.02     0.533    0.008     0.017    0.029   0.005
9           0.029  347.000       0.02     0.492    0.014     0.024    0.038   0.006
10          0.037  349.000       0.02     0.491    0.017     0.029    0.043   0.007
11          0.039  358.000       0.02     0.484    0.018     0.030    0.045   0.007
12          0.018  396.000       0.02     0.459    0.010     0.019    0.030   0.005
13          0.028  431.000       0.02     0.438    0.015     0.024    0.037   0.006
14          0.025  441.000       0.02     0.433    0.013     0.023    0.035   0.005
15          0.027  477.000       0.02     0.414    0.015     0.024    0.036   0.006
16          0.045  484.000       0.02     0.410    0.023     0.035    0.050   0.007
17          0.030  494.000       0.02     0.405    0.016     0.026    0.039   0.006
18          0.022  501.000       0.02     0.402    0.012     0.021    0.032   0.005
19          0.028  505.000       0.02     0.400    0.015     0.025    0.036   0.005
20          0.020  540.000       0.02     0.384    0.012     0.020    0.031   0.005
21          0.028  563.000       0.02     0.374    0.016     0.025    0.037   0.005
22          0.024  593.000       0.02     0.362    0.014     0.022    0.033   0.005
23          0.015  602.000       0.02     0.358    0.010     0.017    0.026   0.004
24          0.024  629.000       0.02     0.348    0.014     0.023    0.033   0.005
25          0.020  636.000       0.02     0.346    0.012     0.020    0.030   0.005
26          0.048  729.000       0.02     0.316    0.027     0.039    0.053   0.007
27          0.031  849.000       0.02     0.284    0.019     0.028    0.038   0.005
28          0.027  914.000       0.02     0.269    0.017     0.025    0.035   0.005
29          0.021  940.000       0.02     0.264    0.014     0.021    0.030   0.004
30          0.029 1193.000       0.02     0.220    0.020     0.027    0.036   0.004
31          0.020 1340.000       0.02     0.201    0.014     0.020    0.027   0.003
colMeans    0.029  517.032       0.02     0.438    0.015     0.025    0.037   0.006
\end{CodeOutput}
\begin{CodeInput}
R> summary(p)
\end{CodeInput}
\begin{CodeOutput}
Main summary:

                  obs.mean        n prior.mean shrinkage intv.low post.mean intv.upp post.sd
Unit w/ min(n)       0.045   67.000       0.02     0.834    0.011     0.024    0.042   0.008
Unit w/ median(n)    0.045  484.000       0.02     0.410    0.023     0.035    0.050   0.007
Unit w/ max(n)       0.020 1340.000       0.02     0.201    0.014     0.020    0.027   0.003
Overall Mean         0.029  517.032       0.02     0.438    0.015     0.025    0.037   0.006

Second-level Variance Component Estimation Summary:
alpha = log(A) for Gaussian and log(1/r) for Binomial and Poisson data:

  post.mode.alpha post.sd.alpha
1          -5.818         0.411
\end{CodeOutput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.3]{hospital1.png}
\caption{Shrinkage and interval plots of 31 hospitals in NY}
\end{center}
\end{figure}
